03 Data Vizualization

### 2022-06-16 03_data_viz.Rmd
time to visible colony plot

>>>>

## (PASSING) Visible colony

```{r}
# Function Definitions
col_volumer <- function(a,b,c) {
  # Volume of a half-ellipsoid of axes a,b, and c
  vol = (4/3)*pi*a*b*c
  vol = vol/2
  return(vol)
}

cell_volumer_rod <- function(a,b,c) {
  vol = a*b*c
  return(vol)
}

cell_volumer_cocci <- function(r) {
  vol = (4/3)*pi*(r^3)
  return(vol)
}

# Define parameters of colony needed to be visible:
xax <-  1000 # x axis, y axis, z axis, in µm
yax <-  1000
zax <-  (1/6)*1000

colony_vol = col_volumer(xax, yax, zax) # generate the volume of a half-ellipsoid, circular base, 1/6th as high as wide

colony_data <- read_csv(file.path('data/bac_data.csv'))
colony_data <- colony_data %>%
  # Calculate cell volumes
  mutate(cell_volume = 
           case_when(shape == 'cocci' ~ cell_volumer_cocci(mjr_axis/2),
                     shape == 'rod' ~ cell_volumer_rod(mjr_axis, mnr_axis, mnr_axis)
                     )
         ) %>%
  # Calculate number of cells required for given volume
  mutate(num_cells_reqd = colony_vol/cell_volume) %>%

  # Calculate number of divisions required to reach visible colony
  mutate(divis_reqd = log2(num_cells_reqd)) %>%

  # Calculate hours required to reach that many divisions
  mutate(time_reqd_hr = divis_reqd*gen_time_hr)

# Get mean value for cells required in single colony
cells_in_single_colony <- colony_data %>% 
  pull(num_cells_reqd) %>% 
  mean()

colony_data_2 <- 
  tibble(gen_time_hr = seq(1, 5000, by = 1),
         num_cells_required = cells_in_single_colony,
         divis_reqd = log2(num_cells_required),
         time_reqd_hr = divis_reqd*gen_time_hr,
         gen_time_d = gen_time_hr / 24,
         time_reqd_d = time_reqd_hr / 24)
```

```{r}
p_time_reqd_for_visible_colony <- colony_data_2 %>% 
  ggplot(aes(x = gen_time_d,
             y = time_reqd_d)) +
  geom_line() +
  geom_vline(xintercept = 60,
             color = tundra_color,
             linetype = "dotted") +
    geom_vline(xintercept = 26,
             color = grassland_color,
             linetype = "dotted") +
    geom_vline(xintercept = 19.4,
             color = conifer_color,
             linetype = "dotted") +
  annotation_logticks(sides = "l") +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x)
              ) +
  theme_classic() +
  labs(
    x = "Maximum potential generation time (days)",
    y = "Time required for visible colony (days)")
p_time_reqd_for_visible_colony

cowplot::save_plot(
  filename = "fig_output/time_for_visible_colony.pdf",
  plot = p_time_reqd_for_visible_colony,
  base_height = 4,
  base_width = 4.5
)
```
